`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

# Critical transition 

 * Author [Carl Boettiger](http://carlboettiger.info), <cboettig@gmail.com>
 * License: [CC0](http://creativecommons.org/publicdomain/zero/1.0/)
 * Description:   

``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````


Chose the state equation / population dynamics function

``` {r }
f <- May
````

With parameters 

``` {r }
pars <- c(r = .75, k = 10, a=1, H=1, Q = 3)
K <- 8 # approx
````

Note that this bifurcates when a increases to 2.  


We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  

<div> $$ \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x}, $$ </div> 

conditioned on h > x and x > 0,

``` {r  profit}
price <- 1
c0 <- 0.0
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

with price = `r price`, `c0` = `r c0` and `c1` = `r c1`. 


``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

We seek a harvest policy which maximizes the discounted profit from the fishery using a stochastic dynamic programming approach over a discrete grid of stock sizes from `r xmin` to `r xmax` on a grid of `r grid_n` points, and over an identical discrete grid of possible harvest values.  


``` {r  grid}
x_grid <- seq(xmin, xmax, length = grid_n)  
h_grid <- x_grid  
````


``` {r miscpars}
delta <- 0.005
xT <- 0
OptTime <- 5000
sigma_g <- .1
````

We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.  The Reed model considers a stochastic growth model 

<div> $$ x_{t+1} = z_g f(x_t) $$ </div> 

for the random variable `z_g`, given by 

``` {r noise}
z_g <- function() rlnorm(1, 0, sigma_g) 
````

No other sources of noise enter into the dynamics.  

``` {r othernoise}
z_m <- function() 1
z_i <- function() 1
````



``` {r  SDP_Mat}
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````


### Find the optimum by dynamic programming

Bellman's algorithm to compute the optimal solution for all possible trajectories.

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
                     profit, delta=delta, reward=0)
````

Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.   


Plot the policy function (in terms of escapement, `x-h`, rather than harvest `h`) at equilibrium (first time-step):

``` {r policyfn_plot}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

and the value function (at equilibrium):

``` {r valuefn_plot}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````

### Simulate 


``` {r simulateme}
Dt <- 1

ForwardSimulate <- 
  function(f, pars, x_grid, h_grid, x0, D, z_g,
         z_m=function(x) 1, z_i = function(x) 1, 
         profit=NULL){

  OptTime <- dim(D)[2]    # Stopping time
  x_h <- numeric(OptTime) # population dynamics with harvest
  h <- numeric(OptTime) # optimal havest level
  x_h[1] <- x0  # initial values
  s <- x_h # also track escapement
  x <- x_h # What would happen with no havest
  p <- numeric(OptTime)

  ## Simulate through time ##
  for(t in 1:(OptTime-1)){

    # Move towards collapse
    pars[3] <- pars[3] + Dt/OptTime



    # Assess stock, with potential measurement error
    m_t <- x_h[t] * z_m()
    # Current state (is closest to which grid posititon) 
    St <- which.min(abs(x_grid - m_t)) 
    q_t <- h_grid[D[St, (t + 1) ]] 
    # Implement harvest/(effort) based on quota with noise 
    h[t] <- q_t * z_i()
    # Noise in growth 
    z <- z_g() 
    # population grows
    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
    s[t+1]   <- x_h[t] - q_t # anticipated escapement
    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
    p[t] <- profit(x_h[t], h[t])
  }
  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
             unharvested = x, escapement = s, profit = p) 
}

dat <- ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
x <- dat$fishstock
```



### Plot of timeseries 

``` {r  p0}
plot(x, type='l')
````

Truncate the timeseries 

``` {r truncate}
y <- x[x > 1.5]
````

``` {r  p1}
plot(y, type='l')
````

### Calculate warning signals on the truncated series. 

``` {r libs2}
library(earlywarning)
dat <- data.frame(time=1:length(y), value=y)
````

``` {r earlywarning}
acor_tau <- warningtrend(dat, window_autocorr)
var_tau <- warningtrend(dat, window_var)

acor_tau
var_tau
````

## Model based statistics


Fit the models

``` {r modelbased}
A <- stability_model(dat, "OU")
B <- stability_model(dat, "LSN")
observed <- -2 * (logLik(A) - logLik(B))
m <- B$pars["m"]


observed
m
````



Compute summary stat versions

``` {r summarystat_roc} 
summarystat_roc <- function(A,B, summarystat_functions, reps=200){
  require(plyr)
  require(reshape2)
  Asim <- simulate(A, reps)
  Bsim <- simulate(B, reps)
  Asim <- melt(Asim, id = "time")
  Bsim <- melt(Bsim, id = "time")
  names(Asim)[2] <- "rep"
  names(Bsim)[2] <- "rep"
	dat <- lapply(summarystat_functions, function(f){
	  wsA <- ddply(Asim, "rep", warningtrend, f)
  	wsB <- ddply(Bsim, "rep", warningtrend, f)
	  data.frame(null = wsA$tau, test = wsB$tau)
	})
	tidy <- melt(dat)
}

dat <- summarystat_roc(A,B, list(var=window_var, acor=window_autocorr))
ggplot(dat) + geom_density(aes(value, fill=variable)) + facet_wrap(~L1)
```




Set up a parallel environment

``` {r parallel}
require(snowfall)
sfInit(par=T, cpu=12)
sfLibrary(earlywarning)
sfExportAll() 
```

Evaluate the ROC curve

``` {r roc}
reps <- sfLapply(1:500, function(i) compare(A, B))
lr <- lik_ratios(reps)
roc <- roc_data(lr)
```

Plot results.

``` {r plotroc}
require(ggplot2)
ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
    geom_vline(aes(xintercept = observed))
ggplot(roc) + geom_line(aes(False.positives, True.positives))
```



