`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="unmanaged_warning/" or`

``` {r  echo=FALSE, cache=FALSE}
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

# Detecting warning signals in an unmanaged system 

This is a precursor exercise to managed_warning.Rmd to calibrate a reasonable set of parameters over which to evaluate the detection.  


``` {r  setup, echo=FALSE, cache=FALSE}
# load required libraries
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````


Simulate from the May population dynamics function



``` {r  simulate }
n <- 5000
x <- vector(mode="double", length=n)
a <- x
x[1] <- 8 # positive equilibrium
z <- rlnorm(n, 0, .1)
r = .75; k = 10; a[1]=1; H=1; Q = 3
for(t in 1:n){
  x[t+1] = z[t] *  x[t] * exp(r * (1 - x[t] / k) - a[t] * x[t] ^ (Q - 1) / (x[t] ^ Q + H ^ Q)) 
  a[t+1] = a[t] + 1/5000
}
````



### Plot of timeseries 

``` {r  p0}
plot(x, type='l')
````

Truncate the timeseries 

``` {r truncate}
y <- x[x > 1.5]
````

``` {r  p1}
plot(y, type='l')
````

### Calculate warning signals on the truncated series. 

``` {r libs2}
library(earlywarning)
dat <- data.frame(time=1:length(y), value=y)
````

``` {r earlywarning}
acor_tau <- warningtrend(dat, window_autocorr)
var_tau <- warningtrend(dat, window_var)

acor_tau
var_tau
````

## Model based statistics


Fit the models

``` {r modelbased}
A <- stability_model(dat, "OU")
B <- stability_model(dat, "LSN")
observed <- -2 * (logLik(A) - logLik(B))
m <- B$pars["m"]


observed
m
````



Compute summary stat versions

``` {r summarystat_roc} 
summarystat_roc <- function(A,B, summarystat_functions, reps=200){
  require(plyr)
  require(reshape2)
  Asim <- simulate(A, reps)
  Bsim <- simulate(B, reps)
  Asim <- melt(Asim, id = "time")
  Bsim <- melt(Bsim, id = "time")
  names(Asim)[2] <- "rep"
  names(Bsim)[2] <- "rep"
	dat <- lapply(summarystat_functions, function(f){
	  wsA <- ddply(Asim, "rep", warningtrend, f)
  	wsB <- ddply(Bsim, "rep", warningtrend, f)
	  data.frame(null = wsA$tau, test = wsB$tau)
	})
	tidy <- melt(dat)
}

dat <- summarystat_roc(A,B, list(var=window_var, acor=window_autocorr))
ggplot(dat) + geom_density(aes(value, fill=variable)) + facet_wrap(~L1)
```




Set up a parallel environment

``` {r parallel}
require(snowfall)
sfInit(par=T, cpu=12)
sfLibrary(earlywarning)
sfExportAll() 
```

Evaluate the ROC curve

``` {r roc}
reps <- sfLapply(1:500, function(i) compare(A, B))
lr <- lik_ratios(reps)
roc <- roc_data(lr)
```

Plot results.

``` {r plotroc}
require(ggplot2)
ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
    geom_vline(aes(xintercept = observed))
ggplot(roc) + geom_line(aes(False.positives, True.positives))
```


