---
title: Optimal management of a stochastically varying population when policy adjustment is costly

author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville

abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question -- how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.

layout: preprint

bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle

output:
  pdf_document:
    template: components/elsarticle.latex
    fig_caption: true
---


```{r configure, include=FALSE, cache=FALSE}
#source("components/install.R")

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

fig.cache <- TRUE
```

```{r analysis, include=FALSE}
source("components/analysis.R")
```


Introduction
============


Ecosystems are dynamic and exhibit rich patterns of variability in
both time and space. In designing management policies for ecosystems,
managers need to decide how much of that variation to respond to. Managers
could try to track variations in ecosystem dynamics very closely by
setting policies that are extremely responsive to the environment. Many
theoretical studies that seek to identify optimal policies for exploited
populations and communities adopt this approach and largely ignore the
challenges that would be involved in implementing such recommendations
[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
the policy process can often be much more sluggish
to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2010]. 
Moreover, stakeholders impacted by ecosystem management
may prefer some stability and not want to deal with continually changing
management recommendations [@Biais1995; @Armsworth2003;
@Patterson2007a; @Patterson2007b; @Sanchirico2008].
In other words, whatever gains are available from fine-tuning a
policy prescription to reflect environmental variation more closely
should be traded off against potential costs associated with the more
interventionist approach to management this would require.

To illustrate these concepts, Figure 1 show an example from fisheries
management. On the left axis, the figure shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  On the right axis the figure
also shows the catch quota for the stock that was set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

We use a classic fisheries management question to examine how accounting
for costs of policy adjustment can change optimal policies (see also
@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
harvest quotas for a stochastically varying fish population can be
chosen to maximize the net present value of a fishery. Our formulation
and solution method largely follow Reed's classic treatment on this
question, a treatment repeated widely in bioeconomic textbooks. With
his formulation, Reed showed that a constant escapement policy could be
optimal under certain conditions. Such a policy involves choosing annual
quotas that are perfectly responsive to recruitment variation in a fish
stock. In poor recruitment years, the quota is set to zero and no fishing
is allowed. But any time there is a good recruitment pulse, a quota is
set that allows the fishery to exactly compensate through harvesting,
thereby maintaining the optimal escapement level. However, in that
analysis, Reed did not account for any costs of policy adjustment, which
for such a responsive management strategy potentially could be large.

As the example in Figure 1 makes clear, management policies will rarely be
as responsive as this constant escapement policy assumes. In this paper,
we explore conditions under which this lack of responsiveness may be a
rationale response on the part of managers. Specifically, we consider a
case where managers seek to balance the benefits in terms of increased
profits from fishing from more finely tracking recruitment variations
with the growing costs associated with adjusting policies quickly to do
so. The policy adjustment costs involved could reflect pure administrative
transaction costs or preferences held by fishermen, fish processing plants
or other stakeholders, for less variable quotas. In seeking to account
for these policy adjustment costs, we recognize that we do not know just
what functional form they should take and that it will require a lot of
empirical work to estimate that. Therefore, we scope three candidate
functional forms that represent different assumptions about how these
costs operate to determine whether the results we obtain are sensitive
to such differences.









-   Ecosystem management frequently set in terms of policy of quotas.

-   Policy relatively static and costly to change

-   Meanwhile, the natural world is variable

-   Optimal solutions typically track these shocks, resulting in
    impractical management recommendations in face of policy costs

*Develop a figure to insert here comparing quotas that were set to the
stock size estimated at that time in the stock assessment for two
different fish stocks. We choose the two stocks to highlight variation
in how responsive management can be. Suggested halibut and bluefin
tuna.*

Empirics suggest not always as responsive as Reed solution. Explore
conditions under which that makes sense. Idea is that regulator's
objective sometimes may not be 'raw' NPV, but rather NPV with some
penalties on fast changes. Possible reasons: pure administrative
transaction cost of changing policies (reaching agreement), fishermens'
preferences for less variable quotas, processing plants' preferences for
less variable quotas especially if tied into contracts for canning and
so forth. But we do not know what functional form of any such policy
adjustment costs takes and it will be a lot of work to estimate it. Here
we explore several plausible candidate functional forms that each
reflect different ways these policy adjustment costs could work. Would
be good to know if differences between functional forms is particularly
important.

Methods
=======

Fish population dynamics / state equation. We will assume Beverton-Holt
dynamics with multiplicative environmental noise

$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$

where $N_t$ the stock size, $h_t$ the harvested level, 
$Z_t$ gives the stochastic shocks, which we
assume are lognormally distributed and $A$ and $B$ are positive
constants. 

We assume managers set an annual quota for harvesting $h_t$ (the control
variable) after observing the stock size that year $N_t$ (the state
variable), but while still being uncertain about future environmental
conditions and stock sizes. Through time, this gives a time path of
management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock
sizes that were observed (a state dependent control rule).

We assume that managers choose annual quotas to maximize the expected
net present value (NPV) of the fishery. We take as a base case the
situation where there are no costs associated with policy adjustment and
the managers' objective is


\begin{equation}
\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right) \label{eq:objective}
\end{equation}

where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the
discount rate and $\Pi_0$ is the net revenue from operating the fishery
in a given year. In this base case, we assume the annual net revenue
from fishing is

\begin{equation}
\Pi_0(N_t,h_t) = p h_t -  c_0 E_t \label{eq:annual_netrevenue}
\end{equation}

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$. (Examples 
shown here use $p$= `r price` and $c_0$ = `r c0`.) 
<!-- Mention R code provided to test other values? Do we need to test other values?
(i.e. the c0 = 0 case?) Word about units?-->

Taken together this objective function \eqref{eq:objective} and the state
equation \eqref{eq:state_equation} define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $h_0^{\ast}$. 

We solve this problem on a finite time horizon of $T =$ `r OptTime` using
value iteration [@Mangel1988; @Clark2000]. 



Costs of policy adjustment {#costs-of-policy-adjustment .unnumbered}
--------------------------

We compare this base case to three alternative problem formulations,
each reflecting different plausible functional forms that costs of
policy adjustment could take. In each, we assume managers can adjust the
quota set in the fishery $h_t$ in a given year and that any policy
adjustment costs are associated with changes to this control variable.

First we assume that policy adjustment costs are directly proportional
to the magnitude of the change in policy being proposed, such that
larger changes to annual harvesting quotas incur greater policy
adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$
equation with

$$\Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.$$

Next we continue to assume that policy adjustment costs depend on the
magnitude of the change in policy being proposed. However, we consider a
case where this dependence is nonlinear with big changes in policy being
disproportionately expensive:

$$\Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.$$

Finally, we assume instead that there is a fixed cost associated with
any adjustment of policy, regardless of how large that adjustment might
be

$$\Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,$$

where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if
$h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a
new objective function $NPV_i$ similar to that in Eqn. \eqref{eq:objective}.

Taken together with the state equation Eqn. \eqref{eq:state_equation}, each
of these new objective functions defines a different stochastic dynamic
programming problem. Again, we solve them numerically using backwards
recursion. To include costs of policy adjustment, we expand the state
space to include both the current stock size and the management action
taken on the previous time step $(N_t,h_{t-1})$. For each new objective
function $\max NPV_i$, we denote the corresponding optimal control
policy $h_i^*$.


In addition in the Supplementary Material, we compare our results with 
more conventional fisheries economic formulation in which additional
costs are applied to the control variables themselves, as opposed to
adjustments to the controls: $\Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this form tend to have a smoothing effect on optimal quotas, but also change
the long-term average stock size or quota size that is optimal.

Choice of parameters {#choice-of-parameters .unnumbered}
--------------------

<!--NOTE c_i notation is confusing because it does not usually refer to c_0 or c_4 -->
Each of the policy adjustment cost function is characterized in terms of
a cost coefficient $c_i$. However, $c_i$ takes different units for each
functional form. Therefore, if seeking to compare the relative effect of
each penalty function on optimal management, it is unclear what
parameter values should be used. To address this issue, we calibrate
choices of $c_i$ so that each has a comparable impact on the optimal net
present value of fishery, broadly following the example of Bovenberg,
Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).
<!--NOTE Jake to confirm these are still relevant and needed. We are using a less sophisticated normalization than was once discussed and may or may not need the citations now. -->

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs.

```{r Figure_2, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.  The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("penalty coefficient") +
  ylab("Reduction in net present value") 

```


To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth 80% of its
unconstrained value when optimally managed.

We focus our examination of the models on how the type and severity of
policy adjustment costs affects the optimal management strategy. To
simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 100; specifically, $A=2$ and
$B=0.01$ in Eqn. (1)). To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed HOW? In addition, we
show cases where $p=1$, $\delta=0.05$ and $c_0$ is chosen such that the
optimal stock size in the analogous deterministic problem is 5% larger
than that corresponding to the maximum sustainable yield in biomass
($c_0=XXX$).







Results
=======

Effect of policy adjustment costs on optimal quotas and stock sizes {#effect-of-policy-adjustment-costs-on-optimal-quotas-and-stock-sizes .unnumbered}
-------------------------------------------------------------------



Figure 2 illustrates how the different forms of adjustment cost can
impact the optimal policy. Each panel is generated against the same
sequence of random shocks so that they can be compared directly. Figure
3 shows the corresponding stock sizes, which are measured here before 
harvest ($h_t$ being determined after observing stock size $x_t$).
Because stock sizes are measured before harvests, the effect of the 
penalty on the stock size is not very pronounced, while the effect
on the harvest chosen shows a systematic deviations from the penalty
free optimum, depending on the nature of the cost.  


In each case, the optimal solution without any adjustment cost is shown in
against the policy induced by optimization under the given adjustment
penalty (equivalent to a `r 100*reduction`% reduction in maximum expected NPV) 
is overlaid in blue.


When considering the first formulation of policy adjustment costs
($\Pi_1$), the first panel of Figure 2 shows a typical pattern, in which
the optimal policy tends to avoid small policy adjustments, resulting in
long periods of constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation $\Pi_2$ disproportionately penalizes large policy
adjustments. The corresponding optimal policy tracks all of the changes
made by the cost-free policy, but with smaller magnitude. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty. Whereas the optimal solution for
$\Pi_1$ attempts to accommodate the large oscillations at the end of the
period shown (time steps $t=47-49$) with a constant quota in between the
extremes, the fixed fee version takes the opposite approach of one very
large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8, cache = fig.cache}

fig2_df <- as.data.frame(subset(dt, replicate=='rep_2'))
fig2_df <- fig2_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
fig2_df <- melt(fig2_df, id = c("time", "penalty_fn"))
fig2_df <- data.frame(fig2_df, baseline = fig2_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig2_df$variable <- variable_map[fig2_df$variable]
fig2_df$baseline <- baseline_map[fig2_df$baseline]


ggplot(fig2_df, aes(time, value, col=baseline)) +
  geom_line() +
  facet_grid(variable~penalty_fn) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  


```



The comparisons shown in Figure 2 are for one realization (i.e. a
particular sequence of random number draws representing environmental
variability) and are made for a particular magnitude of policy
adjustment costs equal to `r reduction`% of the maximum expected net present value 
in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show
how optimal harvest levels and corresponding optimal stock sizes are
affected by the magnitude of the costs of policy adjustment. This time
we show summary statistics across 50 replicate sets of environmental
conditions. We show the impact of policy adjustment costs on the
variance of both harvests and stock sizes through time; on the
autocorrelation of harvests and stock sizes through time; and on the
cross-correlation of harvests and stock sizes through time. <!-- NOTE Are we showing cross-correlations or not? --> <!-- See figure 4, probably not-->

For example, when small policy adjustment costs cost little but large
adjustments are expensive ($\Pi_2$), we see the smoothing signal that we
might have expected (see also Ludwig 1980 for this particular case). As
cost penalties increase in severity (i.e., $c_2$ increases), the
variance in quotas through time decreases and the autocorrelation of
quotas through time increases. This smoothing of the harvest quotas
through time has knock-on effects for the corresponding optimal stock
sizes, which also become more autocorrelated as the scaling on policy
adjustment costs ($c_2$) is increased. The autocorrelation in stock
sizes here reflects the lag involved in a more modest increase in
harvests taking longer to eliminate the signal of strong recruitment
events, when compared to a more immediately responsive constant
escapement policy.

Interestingly, as suggested by the realization in Fig. 2, including a
fixed cost of policy adjustment increases the variation in harvests
through time. This is the opposite of a smoothing effect. Follow-on
consequences for the other statistics are not as clear in this case.

Finally, the case where policy adjustment costs scale linearly with the
size of the adjustment ($\Pi_1$ in Eqn. 4) appear to be something of a
middle of the road strategy, in that increasing the severity of policy
adjustment costs (increasing $c_1$ has little effect on the variance or
autocorrelation of optimal harvest rates or stock sizes. To reveal the
particular impact of policy adjustment costs of this type requires a
more targeted summary statistic. Specifically, for each run we
calculated the frequency with which the optimal policy involved
maintaining a positive quota across multiple time steps unaltered. This
type of policy is arguably the most commonly observed behavior in TAC
management, but is one that is almost never observed to be part of the
optimal management strategy in the basic model without policy adjustment
costs (Eqn. 3) or when optimizing against $\Pi_2$ or $\Pi_3$. While
still not common for the particular parameter combinations we examine,
we find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes (STATISTIC).
Moreover, these occurrences increase in frequency as the severity of
these costs ($c_1$) increases (STATISTIC).


<!--
Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}

with_xcor_plot <- 
ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  facet_wrap(~variable, scales = "free_y") +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line")
with_xcor_plot
```

-->





```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_wrap(~ timeseries + statistic, scale="free_y")

```



Consequences of policy adjustment costs {#consequences-of-policy-adjustment-costs .unnumbered}
---------------------------------------

Next we examine the consequences either of ignoring policy adjustment
costs when they are present or assuming they are present when they are
not. To do so, it helps to break-down the different contributions to the
maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$
versus when employing the policy that would be optimal were there no
costs to policy adjustment $\bf{h_0}^*$. For example, if we take the
first of the adjustment penalty forms, $\Pi_1$

$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

and

$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

Histograms for the different contributions labelled $[1]-[4]$ here when
taken across XXX replicate runs are shown are shown in Figure 5
(contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The
cost of assuming policy adjustments are present when in fact they are
absent is given by subtracting the contribution to the first infinite
sum from term $[1]$ from the contribution to the second infinite sum of
term $[3]$ (blue - red in the Figure). (Note that convergence properties
required to do this are met because we assume a positive discount rate).
This cost is positive because the optimal controls recommended when
assuming policy adjustment costs are present do not track variations in
stock size as closely. Therefore, this harvesting strategy provides
lower net revenue dockside.

In contrast, the cost of ignoring policy adjustment costs when in fact
they are present is given by subtracting the second infinite sum from
the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These
costs are positive because the lost revenues from not tracking stock
variations as closely are smaller than the penalties of policy
adjustment that are incurred if managers try to track stock variations
more tightly.

**


Table 1 compares these different contributions, namely the $NPV$ lost by
assuming policy adjustment costs when none are present (first entry in
each cell, $[3]-[1]$ in the equations)) and the $NPV$ lost when
ignoring policy adjustment costs when they are present (second entry in
each cell of the table, contributions $([1]-[2])-([3]-[4]))$ in the
equations) across the three different functional forms. Specifically,
the table shows how these values change as we vary the severity of
policy adjustment costs. In each case, values are shown as percentages
of the maximum expected $NPV$ in the base case where no policy
adjustment costs apply or are assumed to apply $NPV_0({\bf h_0^*})$. For
a sensitivity test where we draw similar comparisons for different
amounts of environmental variation, see Supplementary Information X.X.

We find a pronounced asymmetry when comparing the impact on the net
present value of the fishery of assuming policy adjustment costs are
present when they are absent with the impact of assuming they are absent
when they are present. For all three types of policy adjustment cost,
the impact on NPV of ignoring these costs if they are in fact present is
much bigger than that incurred by fallaciously managing as if they are
present when they do not occur. This asymmetry arises, because there is
less difference in the dockside revenue under the two management
recommendations than there is in the potential policy adjustment costs
themselves, as is evident in for the particular parameters shown in
Figure 5.

We also see that the impacts on net present value of the fishery of
incorrectly assuming or ignoring policy adjustment costs are most severe
when these costs are assumed to scale quadratically with the size of the
policy change being implemented ($\Pi_2$).


```{r table-caption}
caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic (L2) costs."
```

```{r Table1, results="asis"}
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
pandoc.table(table1, caption=caption)
```

```{r Table1-Figure, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
```

<!--
NOTE Obviously we have presentation choices to make here. I think there is plenty of scope either to compact this table somehow (rows are penalty functions)  x columns are percent reduction.

There would also be lots of scope for showing the same info visually as a simple bar chart
-->







Discussion
==========

TO COME PENDING WHAT THE RESULTS SHOW.

-   From Meeting 3: Interest in how the inclusion of these costs would
    operationally put a population at greater risk of extinction (e.g.
    if including the transaction costs increases the variance and
    autocorrelation of $N$ when subject to the optimal policy). Should
    expect this, because as the transaction costs become infinite, you
    would never change your policy which puts you in the world of open
    loop control - TAC fixed for all time, which we know puts the stock
    at greater risk of extinction.

-   On Table 1 should flag that might also be good to look at
    autocorrelated environmental noise and how that affects thing. Here
    we look at how the optimal policy induces more color in the stock
    size EVEN though the environmental variability going into it is
    white noise. - QUERY - HOW MUCH AUTOCORRELATION INDUCED BY STOCK
    DYNAMICS IN THE ABSENCE OF HARVESTING

-   for case of bluefin, interpreting (1), (2), (3), and (4) in terms of
    how much you would have available to pay the Japanese and Canadians
    to convince them to participate in an expedited process to change
    TACs. Similarly for other contexts.

-   Comparison of the optimal policy solution to the Reed model,
    traditional economic smoothing penalty - which now appears in SI

-   Comparison between the different functional forms -- smoothing (L2)
    non-smoothing (L1), and de-stablizing (fixed).

-   Induced costs (relative to free adjustment) vs direct costs (paid
    for adjusting)

-   Contrast steady-state results to dynamic solutions under stochastic
    shocks.

**Key conclusions:**

1.  **Lesson for modelers**: Ignoring the reality of policy costs leads
    to less effective management (decreased value) (increased extinction
    risk?)

2.  **Lesson for policy makers**: Decreasing adjustment costs not only
    saves direct costs, but permits higher-value solutions.



Supplementary material
======================



```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8, cache=fig.cache}

fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 1:5)))
fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
fig1s_df <- melt(fig1s_df, id = c("time", "penalty_fn", "replicate"))
fig1s_df <- data.frame(fig1s_df, baseline = fig1s_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig1s_df$variable <- variable_map[fig1s_df$variable]
fig1s_df$baseline <- baseline_map[fig1s_df$baseline]


ggplot(fig1s_df, aes(time, value, col=baseline, lty=replicate)) +
  geom_line() +
  facet_grid(variable~penalty_fn) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  


```



# References
